A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-04 manuscript.Rmd
remove space in code chunk header closes #29

* do research
* do more research
* spend time with family
"
cat("``` markdown", markdown_example, "```", sep = "")
```

@@

``` markdown
<!--this is a Markdown file -->

@@

```{r, results='asis', echo=FALSE}
model_truth <- combine(
  measurement(
    "MACH",
    items("x", 9),
    loadings = round(loadings_jones_paulhus * 0.7, 2)
    ),
  intercepts("MACH", list(0, 0.2))
  )
cat("``` r",
    model_truth,
    "```",
    sep = "\n")
model <- combine(measurement(
  "MACH",
  items("x", 9)),
  intercepts("MACH", list(0, "NA")))
```

@@

``` r
usethis::browse_github_issues()
```

@@

``` r
# do not run:
gert::git_add(c("manuscript.Rmd", "references.bib"))
gert::git_commit("explain the basics of issues #20")
```

@@

``` r
usethis::create_from_github("aaronpeikert/repro-tutorial", fork = TRUE)
```
In this copy you then make any changes you want.
You could then request that we (or anyone with write permissions) "pull" these changes.
You can view new pull request for any project with:

``` r
usethis::browse_github_pulls()
```

@@

``` r
usethis::pr_init("myrevision")
```

@@

``` r
usethis::pr_push()
```

@@

``` r
automate_make()
```

@@

``` bash
# this should be run in the terminal
make README.md
```

@@

``` bash
# this should be run in the terminal
make
```

@@

``` r
automate_docker()
```

@@

``` bash
make docker
```

@@

``` bash
# this should be run in the terminal
make DOCKER=TRUE
```

@@

``` bash
make SINGULARITY=TRUE
```

@@

``` bash
# this should be run in the terminal
git clone https://github.com/aaronpeikert/repro-tutorial.git
cd repro-tutorial
```

@@

``` bash
# this should be run in the terminal
make docker &&
make -B DOCKER=TRUE 
```

>>>>

* do research
* do more research
* spend time with family
"
cat("```markdown", markdown_example, "```", sep = "")
```

@@

@@

```{r, results='asis', echo=FALSE}
model_truth <- combine(
  measurement(
    "MACH",
    items("x", 9),
    loadings = round(loadings_jones_paulhus * 0.7, 2)
    ),
  intercepts("MACH", list(0, 0.2))
  )
cat("```r",
    model_truth,
    "```",
    sep = "\n")
model <- combine(measurement(
  "MACH",
  items("x", 9)),
  intercepts("MACH", list(0, "NA")))
```

@@

```r
usethis::browse_github_issues()
```

@@

```r
# do not run:
gert::git_add(c("manuscript.Rmd", "references.bib"))
gert::git_commit("explain the basics of issues #20")
```

@@

```r
usethis::create_from_github("aaronpeikert/repro-tutorial", fork = TRUE)
```
In this copy you then make any changes you want.
You could then request that we (or anyone with write permissions) "pull" these changes.
You can view new pull request for any project with:

```r
usethis::browse_github_pulls()
```

@@

```r
usethis::pr_init("myrevision")
```

@@

```r
usethis::pr_push()
```

@@

```r
automate_make()
```

@@

```bash
# this should be run in the terminal
make README.md
```

@@

```bash
# this should be run in the terminal
make
```

@@

```r
automate_docker()
```

@@

```bash
make docker
```

@@

```bash
# this should be run in the terminal
make DOCKER=TRUE
```

@@

```bash
make SINGULARITY=TRUE
```

@@

```bash
# this should be run in the terminal
git clone https://github.com/aaronpeikert/repro-tutorial.git
cd repro-tutorial
```

@@

```bash
# this should be run in the terminal
make docker &&
make -B DOCKER=TRUE 
```
